\subsubsection{Dexguard} \label{subsubsection:counter-reengineering-optobf-dexguard}
%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT


%
A commercial Android obfuscator [37] working both on bytecode and source code level (should not be mistaken with dexguard analysis tool). Performs various techniques including strings encryprion, encrypting app resources, tamper detection, removing logging code.
\cite{kovachevaMaster}
%


ERWÄHNEN WO IM PROZESS ANGEWENDET\newline


WER HAT ES HERGESTELLT? WAS IST ES? WAS SIND DIE FEATURES? WIE FUNKTIONIERT ES? WIE WIRD ES IMPLEMENTIERT? WIE SIEHT DAS RESULT AUS (EXAMPLE BILD)\newline

OVERVIEW\newline
son of proguard\newline
the \"standard\" protection\newline
optimizer\newline
shrinekr\newline
obfuscator/encrypter, does not stop reverse engineering\newline
\url{https://youtu.be/6vFcEJ2jgOw?t=643}\newline
WHAT DOES IT DO\newline
everything that proguard does\newline
automatic reflection\newline
strign encryption\newline
asset/library encryption\newline
class encryption(packign)\newline
applciation tamper protection\newline
file-see-automatic reflection-see-string encryption-see-file\newline
\url{https://youtu.be/6vFcEJ2jgOw?t=745}\newline
class encryption= packer, unpackers do it most of the time in few seconds, aber aufwand auf handy, nicht so einfach wie pattern in luckypatcher\newline
CONS\newline
may increase dex size, memory size; decrease speed\newline
removes debug information\newline
string, etc encryption\newline
best feature: automatic reflection with string encryption\newline
reversible with moderate effort\newline
hacker protection factor 1\newline

ESULT -see- UNTERSCHIED ZU DEN VORHERIGEN -see- The obfuscation methods used in Allatori(dexguard) are a superset of ProGuards so it is more powerful but does not prevent an analyst from disassembling an Android application.
