\subsubsection{Allatori} \label{subsubsection:counter-reengineering-optobf-allatori}
%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT


ERWÄHNEN WO IM PROZESS ANGEWENDET\newline

WER HAT ES HERGESTELLT? WAS IST ES? WAS SIND DIE FEATURES? WIE FUNKTIONIERT ES? WIE WIRD ES IMPLEMENTIERT? WIE SIEHT DAS RESULT AUS (EXAMPLE BILD)\newline

\url{http://www.allatori.com/clients/index.php}\newline

Allatori is a commercial product from Smardec.\newline
Besides the same obfuscation techniques like ProGuard, shown in section 2.1, Allatori also provides methods to modify the program code. Loop constructions are dissected in a way that reverse engineering tools cannot recognize them. This is an approach to make algorithms less readable and add length to otherwise compact code fragments. Additionally, strings are obfuscated and decoded at runtime. This includes messages and names that are normally human readable and would give good suggestions to analysts.\newline

cannot recognize them.
WHAT DOES IT\newline
name obfuscation\newline
control flow flattening/obfuscation\newline
debug info obfuscation\newline
string encryption\newline
RESULT\newline
decreases dex size, memory, increases speed\newline
remvoes debug code\newline
not much obfuscation\newline
Proguard+string encryption\newline
easily reversed\newline
hacker protection factor 0.5\newline
\url{https://youtu.be/6vFcEJ2jgOw}


\url{https://net.cs.uni-bonn.de/fileadmin/user_upload/plohmann/2012-Schulz-Code_Protection_in_Android.pdf}\newline
Allatori [6] is a commercial product from Smardec. Besides the same obfuscation techniques
like ProGuard, shown in section 2.1, Allatori also provides methods to modify the
program code. Loop constructions are dissected in a way that reverse engineering tools
cannot recognize them. This is an approach to make algorithms less readable and add
length to otherwise compact code fragments. Additionally, strings are obfuscated and decoded
at runtime. This includes messages and names that are normally human readable
and would give good suggestions to analysts.
The obfuscation methods used in Allatori are a superset of ProGuards so it is more
powerful but does not prevent an analyst from disassembling an Android application\newline
Allatori. Allatori obfuscator. Visited: May, 2012. [Online]. Available: \url{http://www.allatori.com/doc.html}


RESULT -> UNTERSCHIED ZU DEN VORHERIGEN -> The obfuscation methods used in Allatori are a superset of ProGuards so it is more powerful but does not prevent an analyst from disassembling an Android application.
