
\subsubsection{Dexguard} \label{subsection:counter-obfuscation-solution-dexguard}
\textit{DexGuard} is a commercial Android obfuscator for Java code.
It is considered the offspring of \textit{ProGuard} and specialized on Android.
The provided methods are a super set of \textit{ProGuard}'s ones. \cite{strazzareLevel0}
\newline
In addition to the obfuscation, \textit{DexGuard} offers application and platform integrity, resource protection, communication hardening and code protection \cite{dexguard}.
This way, the application is not only fortified against code analysis but also reverse engineering.
\newline
The side effect of using \textit{DexGuard} is that the application becomes smaller and the performance is increased by the smaller memory usage.

\subsubsection{Allatori} \label{subsection:counter-obfuscation-solution-allatori}
\textit{Allatori} is a commercial Android obfuscator from Smardec.
Similar to \textit{DexGuard} it provides a superset of \textit{ProGuard}'s methods. \cite{allatori}
\newline
The features of \textit{Allatori} include name obfuscation, string encryption and debug information obfuscation.
Even flattening of the structure and obfuscation of the control flow are possible.
Another feature is the addition of complexity to algorithms, e.g. loops are modified in a way that reverse engineering tool do not recognize them as such.
\cite{strazzareLevel0} \cite{allatoriDoc}
\newline
Overall, the resulting application has a decreased \gls{dex} file and memory footprint while having increased speed.
