\section{Motivation}\label{section:introduction-motivation}
Licensing is present in Android as well.
According to Google's in September 2015 there were over 1.4 billion active devices in the last 30 days and a market share of almost 82.8\% in Q2 of 2015 \cite{androidDevices}\cite{androidShare}.
This giant number of Android devices is powered by Google Play \cite{googlePlay}, Google's marketplace.
It offers different kinds of digital goods, as movies, music or ebooks, but also hardware.
In the application section of Google Play user can chose from over 1.6 million applications for Android \cite{statistaAppStore}.
In 2014 Google's marketplace overtook Apple's Appstore, which had a revenue of over 10 billion in 2013, and became the biggest application store on a mobile platform \cite{wiwoValue}.
\newline
The growth has many advantages.
Some time ago developers only considered iOS user as profitable and thus most applications were developed for Apple's \gls{os}.
Now with this reach and potential users they also focus on Android\cite{businessProfit}.
But there are downsides as well.
The expanding market for Android, offering many high quality applications, also draws the attention of software pirates.
Crackers do not only to bypass license mechanisms and offer applications for free.
Redirecting cash flows or distributing malware using plagiates is an lucrative business model as well.
Android developers are aware of the situation \cite{developersPiracy} and express their need to protect their \gls{ip} on platforms like xda-developers \cite{xdaPiracy} or stackoverflow \cite{stackoverflowPiracy}.
Many of the developers having problems with the license verification mechanism name Lucky Patcher as one of their biggest problems \cite{stackoverflowLucky}.
\newline
\newline
The scope of this thesis is to analyse Android cracking applications and to investigate in counter measurements for developers.



%spreading causes giant market (zahlen) -see- google play with big financial value (zahlen)\newline
%je größer der markt desto attraktiver für cracker da auch mehr leute die app ggfs gecracked runterladen würden (genauere argumente)\newline
%deswegen auch gesteigertes interesse bei developern ihre app und IP zu schützen\newline
%when searching for luckypatcher it is often named as a problem

%enthält als Abschluss SCOPE\newline
%so what are effective counter measurements for developers to fight android cracking tools like luckypatcher

%START TEXT INPUT

%
%android grows thus becomes lucrative, increased interest from software pirates
%according to press conference google,2015-09-29, 1.4 billion active devices in last 30 days, counted in the last 30 days\cite{androidDevices}
%market share 82.8 percent \cite{androidShare}
%1.6 mio apps \cite{statistaAppStore}
%2013 Apple 10 billion revenue \cite{statistaRevenue}, 2014 overtaken by google play \cite{wiwoValue}

%developers know from piracy\cite{developersPiracy}
%studies for plagiarism in Play Store

%
