\subsubsection{Unique Implementation} \label{subsection:counter-modifications-library}
\gls{luckypatcherg}'s attack is reliant on successfully applying the patching patterns.
For this reason, actively avoiding these patterns should always be the first step to challenge \gls{luckypatcherg}.
This approach is only possible when using the \gls{lvl}, as it requires access to the source code of the license verification mechanism.
Modifying and improving the \gls{lvl} does not only protect from patterns used by \gls{luckypatcherg}, increasing complexity of the application's bytecode makes it unique and harder to reengineer.
In fact, modifying the lvl is what google strongly suggests.\cite{developersSecuring}
\newline
There are three areas the developer should focus on when modifying the \gls{lvl}  \cite{developersSecuring}.
\begin{enumerate}
\item core licensing library logic
\item entry and exit points of the licensing library
\item invocation and handling of the response
\end{enumerate}
The core logic’s two main classes are the \textit{LicenseChecker} and the \textit{LicenseValidator}.
As seen in section~\ref{section:luckypatcher-patterns}, these two classes are the primary target of \gls{luckypatcherg} and thus should be altered as hard as possible while retaining the original function.
Isomorphic code changes can include:
\begin{itemize}
\item replacing the switch statement with an if statement and add additional code between the if statements (see pattern N1)
\item deriving new values for constants and check for these values in the further proceeding (see pattern N3)
\item removing unused code for interfaces, e.g. implementing the policy verification inline in the \textit{LicenseValidator} instead over an interface (see patterns N2, N4, N5 and N6)
\item move the \gls{lvl} package into the application (see patterns N2 and N7)
\item implementing functions inline where possible (see patterns N2, N5 and N7)
\item making actions in the decompiled code difficult to trace by moving routines to unrelated code, counter intuitive from traditional software engineering
\item implement radical response handling, e.g. killing the application without a hint as soon as an invalid server response is detected, results in bad user experience
\end{itemize}
These are only examples and creativity is welcome since the resulting implementation should be unique. \cite{developersSecuring}
\newline
The entry and exit points can be attacked by creating a counterfeit version of the \gls{lvl} that implements the same interface.
A unique implementation provides resilience against this attack.
It can be achieved by adding additional arguments to the \textit{LicenseChecker} constructor as well as the \textit{allow()} and the \textit{dontAllow()} methods. \cite{developersSecuring}
\newline
Attackers do not only target the \gls{lvl}, but the handling of the result in the application.
This can be prevented by handling the mechanism in a separate activity.
This prevents from scenarios where the attacker voids methods which would prevent further proceeding, e.g. the
In addition, the license verification can be postponed to a later point in time since attackers are expecting it on the the applications launch. \cite{developersSecuring}
\newline
These modifications are easy to apply and make the implementation unique.
There are unlimited ways to implement them.
It needs to be stated, that they are as easily reengineered and patched, but this makes it hard to attack automatically with an universal solution.
A determined attacker, willing to invest time and work in disassembling and reassembling, can eventually find a weakness in the code.
This is the usual race of arms between making things secure and finding new ways to break them.
The gained knowledge can be used to create a custom patch for \gls{luckypatcherg}, cracking the application.
The aim of the developer is to make the work of the attacker as hard as possible to the point where the profit is not worth the time. \cite{developersSecuring}
