\subsubsection{androguard} \label{subsection:forensics-tools-java-androguard}
%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT

%
An analysis and disassembling tool processing both Dalvik bytecode and optimized bytecode\newline
DAD which is also the fastest due to the fact it is a native decompiler, WAS ist dad? ERKLÄREN? .dex files was performed with DAD, the default disassembler
in the Androguard analysis tool, largest successful disassembly
ratio\newline
underlying algorithm is recursive traversal\newline
Androguard has a large online open-source database with known malware patterns\newline
\cite{kovachevaMaster}
%




\url{https://github.com/androguard/androguard}

powerful analysis tool is Androguard\newline
includes a disassembler and other analysis methods to gather information about a program\newline
Androguard helps an analyst to get a good overview by providing call graphs and an interactive interface -see- habe nur CLI benutzt\newline
The integrated disassembler also uses the recursive traversal approach for finding instructions like baksmali, see section 2.2\newline
one most popular analysis toolkits for Android applications due to its big code base and offered analysis methods -see- quelle, warum\newline


RESULT OUTPUT
code Listing

SCRIPT (LISTING BENUTZEN UND RICHTIGE APP)
%python ~/Google\ Drive/master_thesis/sourcefiles/_tools/androdd.py -i ~/Google\ Drive/master_thesis/sourcefiles/lvl/auto/apk-fkupdater/fkupdater.apk -o ~/workspace/master-code-applications/code-fkupdater-lvl-auto/java/androguard/

SCRIPT (LISTING BENUTZEN UND RICHTIGE APP)
\lstinputlisting[
  float=h,
  breaklines=true,
  captionpos=b,
  frame=single,
  numbers=left,
  language=bash,
  linerange={7-9},
  firstnumber=1,
  caption={Script to decompile to Java using androguard},
  label={codeSnippet:androguardScript}
]{data/extractScript.sh}

\begin{lstlisting}[
  float=h,
  basicstyle=\footnotesize,
  breaklines=true,
  captionpos=b,
  language=Java,
  frame=single,
  caption={Java code example using androguard},
  label={codeSnippet:androguardOutput}
]
private void doCheck()
{
    this.mCheckLicenseButton.setEnabled(0);
    this.setProgressBarIndeterminateVisibility(1);
    this.mStatusText.setText(2131099673);
    this.mChecker.checkAccess(this.mLicenseCheckerCallback);
    return;
}
\end{lstlisting}
EXAMPLE BESCHREIBEN code snippet~\ref{codeSnippet:androguardOutput}


jedes tool:\newline
woher kommt es?\newline
wozu wurde es erfunden?\newline
wer hat es erfunden? quelle\newline
blabla von der seite\newline
wozu benutze ich es?\newline
welches abstrahierungslevel\newline
beispiel\newline
additional features?\newline
WARUM SCHAUEN WIR ES UNS AN?\newline
wo findet man es?\newline
welches level?\newline
vorteil\newline
blabla aus dem internet\newline
