\subsection{Signature}\label{subsection:counter-tampering-signature}

%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT


\url{http://developer.android.com/tools/publishing/app-signing.html}\newline
\url{http://forum.xda-developers.com/showthread.php?t=2279813&page=5}\newline

CONTRA\newline


The unfortunate side effect of Lucky Patcher working with the Dalvik cache of an app is that the app developers cannot detect manipulations to their code through fingerprinting because the orig- inal code, located in “/data/app/<appName.apk>/classes.dex”, remains untouched. While it is allowed for an app to access its own optimized bytecode from the cache [32], computing a checksum or a hash for it doesn’t make sense because many optimizations to this bytecode are device-specific and cannot be known in advance.
\cite{munteanLicense}
!!!überprüfen!!!


\subsubsection{Local Signature Check} \label{subsubsection:counter-tampering-signature-local}
%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT



WAS IST DIE IDEE DAHINTER? WIE FUNKTIONIERT ES? WIE WIRD ES IMPLEMENTIERT? WIE SIEHT DAS RESULT AUS (EXAMPLE BILD)\newline

local check whether signature is allowed\newline
once in code \newline
save to use signature in code?\newline

\lstinputlisting[
  basicstyle=\footnotesize,
  breaklines=true,
  captionpos=b,
  frame=single,
  numbers=left,
  language=Java,
  linerange={51-74},
  firstnumber=51,
  caption={Partial Listing},
  label={lst: luckycode}
]{data/4-countermeasurements/1-tampering/5-signature.java}

---> was passiert wenn odex?

\subsubsection{Remote Signature Verification and Remote Code Loading} \label{subsubsection:counter-tampering-signature-remote}
%START TEXT INPUT
This is my real text! Rest might be copied or not be checked!
%START TEXT INPUT



WAS IST DIE IDEE DAHINTER? WIE FUNKTIONIERT ES? WIE WIRD ES IMPLEMENTIERT? WIE SIEHT DAS RESULT AUS (EXAMPLE BILD)\newline

certificate an server, get signature and send to server\newline
content direkt von server laden (e.g. all descriptions, not sure if dex possible)\newline
maps checks for signature?\newline
e.g. account auf seite erstellen, ecrypted dex ziehen der von loader stub geladen wird (like packer)
kann wiedermal dann gezogen werden und dann als custom patch verteilt werden\newline
